### 2013-05-28 talk/slides.tex
Talk for labgroup

\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{times}
\usepackage[T1]{fontenc}
%\usepackage{graphicx}
\usepackage{movie15}  % For embedding movies http://pages.uoregon.edu/noeckel/PDFmovie.html
\usepackage[normal,tight,center]{subfigure}
\usepackage{epstopdf}
\usepackage{colortbl}
%\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `basename #1 .tif`.png}
\definecolor{grey}{rgb}{0.5, 0.5, 0.5}

@@

\title[] % (optional, use only with long paper titles)
{ }
\author%[D~Falster] % (optional, use only with lots of authors)
{Daniel Falster\inst{1}\\
Collaborators: Remko Duursma\inst{2}, Rich FitzJohn\inst{1}, Diego Barneche\inst{1}, many others }
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different affiliation.

@@

\section{Problem} \subsection{intro}
\begin{frame}[c]  \frametitle{}
\end{frame}

>>>>

\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{times}
\usepackage[T1]{fontenc}
%\usepackage{graphicx}
\usepackage[normal,tight,center]{subfigure}
\usepackage{epstopdf}
\usepackage{colortbl}
%\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `basename #1 .tif`.png}
\definecolor{grey}{rgb}{0.5, 0.5, 0.5}

@@

\title[] % (optional, use only with long paper titles)
{A biomass and allometry database for woody plants}
\author%[D~Falster] % (optional, use only with lots of authors)
{Daniel Falster\inst{1}
Collaborators: Remko Duursma\inst{2}, Rich FitzJohn\inst{1}, Diego Barneche\inst{1}, many others }
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different affiliation.

@@

%----------------------------------------------------------------------------------------
\section{Motivation} \subsection{intro}
\begin{frame}[c]  \frametitle{}
\vskip5pt
{\Huge \color{structure.fg} Challenge: Modelling plant life cycles }
\end{frame}

%----------------------------------------------------------------------------------------
\begin{frame}[c]  \frametitle{Mechanistic model capturing common processes}
{\tiny   \color{grey} Falster {\em et al}, J Ecol 2011}
\begin{center}
	 \includegraphics[width=\textwidth]{/Users/dfalster/Dropbox/Documents/talks/archive/12_Falster_ESA/analysis/plantModel.pdf}
\end{center}
\end{frame}

% ----------------------------------------------------------------------------------------
\begin{frame}[c]  \frametitle{Two assumptions about biomass allocation}
\begin{center}
	\includegraphics<1>[width=\textwidth]{/Users/dfalster/Dropbox/Documents/talks/archive/12_Falster_ESA/analysis/output/Assumption-2.pdf}
\end{center}
{\tiny   \color{grey} Falster {\em et al}, J Ecol 2011}
\end{frame}%

% ----------------------------------------------------------------------------------------
\begin{frame}[c]  \frametitle{But - what happens at smaller sizes?}
\begin{center}
	\includegraphics<1>[width=\textwidth]{figures/H-A-Aiba-Martin-only.pdf}
	\includegraphics<2>[width=\textwidth]{figures/H-A-Aiba-Martin-all.pdf}
\end{center}
\end{frame}%

% ----------------------------------------------------------------------------------------
\begin{frame}[c]  \frametitle{Problem - few datasets available}

Mostly not suitable 
\begin{center}
\begin{itemize}
		\item Stand avarges (e.g. Niklas \& Enquist; Gentry) \\[\baselineskip] 
		\item small plants (Poorter 2012)\\[\baselineskip] 
		\item Multi-species (Chave 2005)\\[\baselineskip] 
		\item Focus on  DBH and AGB (not so helpful)\\[\baselineskip] 
	\end{itemize}
\end{center}

\pause
But $\ldots$ lots of data in existence
\end{frame}%

% ----------------------------------------------------------------------------------------
\begin{frame}[c]  \frametitle{Liberating data}
\begin{center}
	\includegraphics<1>[width=\textwidth]{figures/H-A-Aiba-Martin-all.pdf}
\end{center}
\end{frame}%

%----------------------------------------------------------------------------------------
\section{Collaboration} \subsection{intro}
\begin{frame}[c]  \frametitle{}
\vskip5pt
{\Huge \color{structure.fg} Idea: A data paper}
\end{frame}

\begin{frame} [c] \frametitle{Contributions so far}
\begin{center}
	\includegraphics[width=0.9\textwidth]{figures/map.pdf}
\end{center}

{\small \color{red} 86 studies, 14156 individuals, 205 locations, 476 species.}
\end{frame}

% ----------------------------------------------------------------------------------------
\begin{frame}[c]  \frametitle{Principles}
\begin{enumerate}
		\item Recognition for contributors \\$\rightarrow$ coauthorship on data paper (only)\\[\baselineskip] 
		\item Public data \\$\rightarrow$ open and unrestricted use, citation credit \\[\baselineskip] 
		\item Transparent data handling \\$\rightarrow$ text and scripts \\[\baselineskip] 
	\end{enumerate}

\end{frame}

% ----------------------------------------------------------------------------------------
\begin{frame}[c]  \frametitle{}
\vskip5pt
{\Huge \color{structure.fg} Mechanics: Scalable and reproducible}
\end{frame}

% ----------------------------------------------------------------------------------------
\begin{frame}[c]  \frametitle{An R package: dataMashR ??}

\end{frame}

%----------------------------------------------------------------------------------------
\section{Overview of dataset} \subsection{intro}
\begin{frame}[c]  \frametitle{}
\vskip5pt
{\Huge \color{structure.fg} The dataset}
\end{frame}

% ----------------------------------------------------------------------------------------
\begin{frame}[c]  \frametitle{First plots}
	\includegraphics<1>[width=\textwidth]{figures/plot-1.pdf}
	\includegraphics<2>[width=\textwidth]{figures/plot-2.pdf}
	\includegraphics<3>[width=\textwidth]{figures/plot-3.pdf} 
	\includegraphics<4>[width=\textwidth]{figures/plot-4.pdf}
	\includegraphics<5>[width=\textwidth]{figures/plot-5.pdf} 
	\includegraphics<6>[width=\textwidth]{figures/plot-6.pdf}
	\includegraphics<7>[width=\textwidth]{figures/plot-7.pdf} 
	\includegraphics<8>[width=\textwidth]{figures/plot-8.pdf}
	\includegraphics<9>[width=\textwidth]{figures/plot-9.pdf}
\end{frame}

%----------------------------------------------------------------------------------------
\section{Future} \subsection{intro}
\begin{frame}[c]  \frametitle{What next}
\begin{center}
\begin{itemize}
		\item Email report to collabortaors \\[\baselineskip] 
		\item Draft data paper \\[\baselineskip] 
		\item Draft dataMashR package and paper \\[\baselineskip] 
		\item Analysis papers \\[\baselineskip] 
	\end{itemize}
\end{center}
\end{frame}
